\documentclass{scrartcl}

\usepackage{resumetemplate}
\usepackage{colors/defaultcolors}
\usepackage{crodriguezresume}

\begin{document}

\begin{flushleft}
\textcolor{resume-gray}{Monterrey, Nuevo Le\'on} \\
\textcolor{resume-name}{\fontsize{35}{40}\selectfont \textbf{Claudio B\normalsize{.} \fontsize{35}{40}\selectfont Rodr\'iguez}} \\
\vspace{-0.05cm}
\textcolor{resume-gray}{\huge \textbf{claudiordgz}}\\
\mobile\enskip\grayfont{+52 1 (81) 13490166}\\
\phone\enskip\grayfont{01 52 8119358682}\\
\href{http://www.claudiordgz.com}{\pencil\enskip\grayfont{claudiordgz.com}}\\
\href{http://careers.stackoverflow.com/claudiordgz}{\stackOverflow\enskip\grayfont{StackOverflow Profile}}
\end{flushleft}

\begin{minipage}[t]{0.69\textwidth}
	\section*{Objective}
		\input{templ/amazon}
		
\section*{Professional Experience}
\ProfessionalItm{http://www.epicor.com/lac/Pages/default.aspx}{Epicor Software}{June 2014 - Current}
	\textbf{Project:} \href{http://www.epicor.com/Products/Pages/Epicor-LaserCat-3.aspx}{LaserCat 3}
	 \begin{itemize}[noitemsep]
		\item Allowed utility to check for updates for all of my customers by developing a cross platform C++ utility.
		\item Created silent installations by migrating installers from exe to msi.
		\item Reduced production time for installations by creating reusable libraries.
		\item Added relative position design to WiX Dialogs by creating parsing utilities in C++.
	 \end{itemize}

\ProfessionalItm{http://www.amige.com}{AMI GE Automation \& Control Innovation}{June 2012 - June 2014}
	\textbf{Project:} \href{http://amige.com/meltshops_technological_controls_digitarc_px3.html}{DigitARC PX3}
	\begin{itemize}[noitemsep]
		\item Reduced size of files being logged by \%60 using Audio Compression.
		\item Prevented errors when changes to crucial features of the system were done by automating C++ and Bash/Batch testing mechanism and automating them using CruiseControl. 
		\item Reduced customer support from 6 man-hr average p/week to 2 man-hr p/month average by creating tutorials for repeated configuration errors, creating tools in Python, and creating Unit Tests for common changed parts.
		\item Created a modify once, publish on different places system for our product manual, automated it in CruiseControl.
	\end{itemize}
	
\end{minipage}
\hfill
\begin{minipage}[t]{0.28\textwidth}
	\begin{flushright}
	\subsection*{Tech}
		\begin{minipage}[t]{0.48\textwidth}
			\begin{flushleft}
				\cplusplus
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{0.48\textwidth}
				\python
		\end{minipage}
		
		\vspace{0.25cm}
		\begin{minipage}[t]{0.70\textwidth}
				\latexprogress
		\end{minipage}
		\vspace{0.15cm}
		\begin{minipage}[t]{0.24\textwidth}
				\begin{center}
					\Large\LaTeX
				\end{center}
		\end{minipage}
		
		\vspace{0.25cm}
		\begin{minipage}[t]{0.70\textwidth}
				\bashbatch
		\end{minipage}
		\vspace{0.15cm}
		\begin{minipage}[t]{0.24\textwidth}
				\begin{tabular}{c}
					\normalsize Bash \\
					\normalsize Batch
				\end{tabular}
		\end{minipage}
		
		\vspace{0.25cm}
		\begin{minipage}[t]{0.70\textwidth}
				\csharp
		\end{minipage}
		\begin{minipage}[t]{0.24\textwidth}
				\begin{center}
					\Large WPF/C\#
				\end{center}
		\end{minipage}
		
		
		\vspace{0.35cm}
		\begin{minipage}[t]{0.70\textwidth}
				\htmlfivebar
		\end{minipage}
		\begin{minipage}[t]{0.24\textwidth}
				\begin{center}
					\Large \html5
				\end{center}
		\end{minipage}
	
	
	\subsection*{Tools}
		\begin{itemize}[noitemsep]
			\item Git
			\item SVN
			\item Autotools
			\item Windows
			\item Linux 
			\item QNX
			\item Visual Studio
			\item WiX Toolset
		\end{itemize}
	\end{flushright}
\end{minipage}

\newpage

\ProfessionalItm{}{GE Consumer \& Industrial}{2008}

\begin{itemize}[noitemsep]
	\item Developed 147 scheduled maintenance tasks, one for each equipment, deployed and trained maintenance and production personnel.  
	\item Trained Purchasing Leader, Technology Leader, Maintenance Leader, and Production Leader in the use of PMPro tool so they could maximize their benefits from Preventive Maintenance.  
\end{itemize}

\section*{Education}
\ProfessionalItm{http://www.itesm.mx/wps/portal?WCM_GLOBAL_CONTEXT=}{Tec de Monterrey}{Monterrey, N.L.}
Master in Science with Specialty in Intelligent Systems (2010)
\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
	\item Member of Professorship of Applied Intelligent Agents in Videogames.
	\item Specialization in Particle Swarm Optimization and Emergent Behavior Algorithms.
\end{itemize}

\noindent
\ProfessionalItm{http://www.itesm.mx/wps/wcm/connect/Campus/HER/Sonora+Norte/}{Tec de Monterrey Campus Sonora Norte }{Hermosillo, Son}
Mechatronics Engineer (2004-2008) 

\section*{Projects}
\subsection*{\href{https://bitbucket.org/claudiordgz/dentalplacecustomeraccess/src}{Dental Place Access Control}}

WPF/Net 4.5 Utility to allow to keep up to date records for customer access control.
 
\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
	\item Allowed my customer to maintain his brand vision by creating a minimal, and beautiful solution for him.
\end{itemize}


\subsection*{\href{http://claudiordgz.github.io/Phoenix2D/}{Phoenix2D Project}}

Open Source project to allow students to develop their own Player to compete in RoboCup Soccer Simulation. Currently redesigning implementation.
\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
	\item Created build system using GNU Autotools.
	\item Created website.
	\item Create documentation.
\end{itemize}

\subsection*{\href{https://github.com/claudiordgz/WixRelativeDialogs/}{WixRelativeDialogs Project}}

Open Source project for creating dialogs using relative positioning, allowing for more flexible production times. (Faster is better).

\begin{itemize}[leftmargin=*]
	\setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
	\item Developed whole functionality, working in adding UI using QT. 
\end{itemize}
	
\end{document}